New seismological constraints on the available parameter space of macroscopic dark matter

### 2016-08-25 Draft.tex

This procedure is repeated for 17 values of $D$ spaced evenly by $100\,\te{km}$. The average fraction of detectable surface area is then
\begin{align}
\scr F = \sum_D\f{\scr F_D D}{D}\,.
\end{align}
If there are $n$ lunar seismometers, suppose each occupies its own HEALPix pixel. Then $\scr N = n/12\times 2^{n_\te{side}}$ is the fraction of the moon which could potentially measure a signal. If $\scr M$ Macros impact the moon, the likelihood of any of them being detected is
\begin{align}
\scr P = 1-\ps{(1-\scr F)(1-\scr N)}^\scr M\,.
\end{align}

>>>>

This procedure is repeated for 17 values of $D$ spaced evenly by $100\,\te{km}$. The average fraction of detectable surface area is then
\begin{align}
\scr F = \sum_D\f{\scr F_D D}{D}\,.
\end{align}
If there are $n$ lunar seismometers, suppose each occupies its own HEALPix pixel. Define $\scr N = 12\times 2^{n_\te{side}}$. Define $m = \scr F\scr N$, the average number of pixels with detectable frequency. If $n+m\geq \scr N$, then detection is guaranteed. Otherwise, if $\scr M$ Macros impact the moon, the likelihood of any of them being detected is
\begin{align}
\scr P = 1-\ps{\f{(\scr N-n)!(\scr N-m)!}{\scr{N}!(\scr N-n-m)!}}^{\scr M}\,.
\end{align}
